---
title: "bethansci"
author: "BY"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
install.packages("blogdown")
```

```{r}
packageVersion("blogdown")
```
Start the Hugo server using blogdown::serve_site() (only once due to the magic of LiveReload).

```{r}
library(blogdown)
new_site(theme = "wowchemy/starter-academic")
```
```{r}
blogdown::new_post(title = "Hi Hugo", 
                     ext = '.Rmarkdown', 
                     subdir = "post")
```
```{r}
blogdown::config_Rprofile() 

options(
  blogdown.serve_site.startup = TRUE,
  blogdown.knit.on_save = TRUE,     
  blogdown.author = "Bethan Young",
  blogdown.ext = ".Rmarkdown",      
  blogdown.subdir = "post"          
)
```
After a restart
```{r}
serve_site()
```

```{r}
file.edit(".gitignore")
```

```{r}
blogdown::check_gitignore()
```
```{r}
blogdown::check_content()
```

change the baseurl there to match where Netlify is publishing your site

```{r}
rstudioapi::navigateToFile("config/_default/config.yaml", line = 3)
```

if exists, opens; if not, creates new
```{r}
blogdown::config_netlify()
```

Anytime you change your subdomain name, you need to update the baseurl in your config.toml file (so I changed mine to baseurl = “ https://apreshill.netlify.com/").

Fonts & Themes
```{r}
rstudioapi::navigateToFile("config/_default/params.yaml")
```

Menus
```{r}
rstudioapi::navigateToFile("config/_default/menus.yaml")
```


Removing widgets
```{r}
rstudioapi::navigateToFile("content/home/hero.md", line = 5, column = 10)
```

Edit widgets
```{r}
rstudioapi::navigateToFile("content/authors/admin/_index.md")
```

Check site
```{r}
blogdown::check_site()
```

```{r}
blogdown::new_post(title = "Hi Hugo", 
                     ext = '.Rmarkdown', 
                     subdir = "post")
```

